\thetitle

### 2022-06-23 thesis/paper.tex
begin translating new intro subsection

\subsection{Previous literature on college admissions}
Some economists have constructed equilibrium models of the college admissions process that feature the student's application decision as a prominent subproblem. Fu (2014), for example, modeled the United States admissions market as a sequential game played by colleges and students. Colleges announce tuition rates, students apply to college, colleges announce admissions decisions and financial aid offers, and lastly, students decide where to enroll. Equilibrium arises when no college can improve its expected utility by modifying its tuition or admissions policy, and no student can improve her expected utility by modifying her application strategy. The ultimate goal of Fu's model was a comparative statics analysis of various hypothetical reforms to the structure of the admissions market; hence, it was adequate to cluster colleges into $m=8$ broad categories. Therefore, though estimating Fu's model required solving a problem similar to \eqref{headlineproblem}, it was a small instance that could be solved by enumerating all possible portfolios.\footnote{Fu's model of student utility uses a cost function in the size of the application portfolio instead of a budget constraint. Since the optimal portfolio in her model must be utility-optimal over portfolios of the same size, solving her student application problem reduces to solving $m$ instances of \eqref{headlineproblem}.} Our study pursues a more general solution.

>>>>

\ifen \subsection{Previous literature on college admissions} \else \subsection{입학 시장을 고려한 선행 연구}\fi
\ifen
Some economists have constructed equilibrium models of the college admissions process that feature the student's application decision as a prominent subproblem. Fu (2014), for example, modeled the United States admissions market as a sequential game played by colleges and students. Colleges announce tuition rates, students apply to college, colleges announce admissions decisions and financial aid offers, and lastly, students decide where to enroll. Equilibrium arises when no college can improve its expected utility by modifying its tuition or admissions policy, and no student can improve her expected utility by modifying her application strategy. The ultimate goal of Fu's model was a comparative statics analysis of various hypothetical reforms to the structure of the admissions market; hence, it was adequate to cluster colleges into $m=8$ broad categories. Therefore, though estimating Fu's model required solving a problem similar to \eqref{headlineproblem}, it was a small instance that could be solved by enumerating all possible portfolios.\footnote{Fu's model of student utility uses a cost function in the size of the application portfolio instead of a budget constraint. Since the optimal portfolio in her model must be utility-optimal over portfolios of the same size, solving her student application problem reduces to solving $m$ instances of \eqref{headlineproblem}.} Our study pursues a more general solution.
\else
경제학 분야에서, 입학 과정의 균형 모형에서 학생의 지원 결정이 중요한 부문제로서 등장한 사례가 있다. 예를 들어 Fu (2014)는 미국 대학 시장을 대학교와 학생이 참여하는 순차 게임으로 모형화하였다. 대학은 등록금을 공지하고, 학생이 대학에 지원하고, 대학이 입학과 장학금 결과를 공개한 다음에 학생이 어디에 진학할지 결정하는 모형이며, 균형 조건은 어떤 학교도 등록금이나 입학 기준을 수정하여 효용을 늘릴 수 없고, 어떤 학생도 지원 전략을 바꿔서 더 좋은 결과를 얻을 수 없을 때다. Fu의 궁극적 목표는 입학 시장의 다양한 개혁에 대한 민감도 분석이었으며, 이를 진행하기 위해 학교를 $m=8$개의 범주로 클러스터링할 수 있었다. 따라서 모형을 추정하는 데에 \eqref{headlineproblem}과(와) 비슷한 문제를 풀었으나 모든 포트폴리오를 검증하는 열거법으로 풀 수 있는 작은 인스턴스였다.\footnote{Fu의 모형에서는 예산 제약 조건 대신 지원 포트폴리오의 크기에 대한 비용 함수를 사용한다. 이때 최적 포트폴리오는 같은 크기의 포트폴리오 중에서 효용이 가장 높은 포트폴리오가 되어야 하므로 이 문제를 푸는 것은 \eqref{headlineproblem}을(를) $m$번 푸는 것과 동등하다.} 본 연구는 더 일반적인 $m$에 대한 해법을 추구한다.
\fi
